Model-based variable selection for regression with highly correlated variables.

### 2014-08-21 www/article.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@811 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

We define a {\it global} neighbourhood space $\mathcal{V}(\boldsymbol{S})$ of $\boldsymbol{S}$ composed by the following four {\it specific} neighbourhood spaces $\mathcal{V}(\boldsymbol{S})=\mathcal{V}_{r+}(\boldsymbol{S})\cup\mathcal{V}_{r-}(\boldsymbol{S})\cup\mathcal{V}_{p+}(\boldsymbol{S})\cup\mathcal{V}_{p-}(\boldsymbol{S})$ describe below:
	\begin{itemize}
	\item {\bf Adding a sub-regression}: a new sub-regression with only one predictor covariate is added to $\boldsymbol{S}$
\begin{equation}
\mathcal{V}_{r+}(\boldsymbol{S}) = \left\{\tilde{\boldsymbol{S}}: \tilde{\boldsymbol{S}}\in\mathcal{S}, (\tilde{\boldsymbol{J}_r},\tilde{\boldsymbol{J}_p})^{1,\ldots,d_r}=(\boldsymbol{J}_r,\boldsymbol{J}_p), \tilde{J}_r^{d_r+1}\in J_f, \tilde{\boldsymbol{J}}_p^{d_r+1}=\{j\}, j\in J_f \right\}.
\end{equation}	
		\item {\bf Removing a sub-regression}: a sub-regression with only one predictor covariate is removed from $\boldsymbol{S}$
\begin{equation}
\mathcal{V}_{r-}(\boldsymbol{S}) = \left\{\tilde{\boldsymbol{S}}: \tilde{\boldsymbol{S}}\in\mathcal{S}, (\tilde{\boldsymbol{J}_r},\tilde{\boldsymbol{J}_p})=(\boldsymbol{J}_r,\boldsymbol{J}_p)^{\{1,\ldots,d_r\}\backslash j}, j\in\{1,\ldots,d_r\} \right\}.
\end{equation}	
	\item {\bf Adding a predictor covariate}: a predictor covariate is added to one sub-regression of $\boldsymbol{S}$
\begin{equation}
\mathcal{V}_{p+}(\boldsymbol{S}) = \left\{\tilde{\boldsymbol{S}}: \tilde{\boldsymbol{S}}\in\mathcal{S}, \tilde{\boldsymbol{J}_r}=\boldsymbol{J}_r, \tilde{\boldsymbol{J}}_p^{j}=\tilde{\boldsymbol{J}}_p^{j} \cup \{h\}, j\in \{1,\ldots,d_r\}, h\in J_f \right\}.
\end{equation}
	\item {\bf Removing a predictor covariate}: a predictor covariate is removed from one sub-regression of $\boldsymbol{S}$
\begin{equation}
\mathcal{V}_{p-}(\boldsymbol{S}) = \left\{\tilde{\boldsymbol{S}}: \tilde{\boldsymbol{S}}\in\mathcal{S}, \tilde{\boldsymbol{J}_r}=\boldsymbol{J}_r, \tilde{\boldsymbol{J}}_p^{j}=\tilde{\boldsymbol{J}}_p^{j} \backslash \{h\}, j\in \{1,\ldots,d_r\}, h\in J_f \right\}.
\end{equation}	
	\end{itemize}

>>>>

We define a {\it global} neighbourhood space $\mathcal{V}(\boldsymbol{S})$ of $\boldsymbol{S}$ composed by the following four {\it specific} neighbourhood spaces $\mathcal{V}(\boldsymbol{S})=\mathcal{V}_{r+}(\boldsymbol{S})\cup\mathcal{V}_{r-}(\boldsymbol{S})\cup\mathcal{V}_{p+}(\boldsymbol{S})\cup\mathcal{V}_{p-}(\boldsymbol{S})$ described below:
	\begin{itemize}
	\item {\bf Adding a sub-regression}: a new sub-regression with only one predictor covariate is added to $\boldsymbol{S}$
\begin{equation}
\mathcal{V}_{r+}(\boldsymbol{S}) = \left\{\tilde{\boldsymbol{S}}: \tilde{\boldsymbol{S}}\in\mathcal{S}, (\tilde{\boldsymbol{J}_r},\tilde{\boldsymbol{J}_p})^{1,\ldots,d_r}=(\boldsymbol{J}_r,\boldsymbol{J}_p), \tilde{J}_r^{d_r+1}\in J_f, \tilde{\boldsymbol{J}}_p^{d_r+1}=\{j\}, j\in J_f \right\}.
\end{equation}	
		\item {\bf Removing a sub-regression}: a sub-regression with only one predictor covariate is removed from $\boldsymbol{S}$
\begin{equation}
\mathcal{V}_{r-}(\boldsymbol{S}) = \left\{\tilde{\boldsymbol{S}}: \tilde{\boldsymbol{S}}\in\mathcal{S}, (\tilde{\boldsymbol{J}_r},\tilde{\boldsymbol{J}_p})=(\boldsymbol{J}_r,\boldsymbol{J}_p)^{\{1,\ldots,d_r\}\backslash j}, j\in\{1,\ldots,d_r\} \right\}.
\end{equation}	
	\item {\bf Adding a predictor covariate}: a predictor covariate is added to one sub-regression of $\boldsymbol{S}$
\begin{equation}
\mathcal{V}_{p+}(\boldsymbol{S}) = \left\{\tilde{\boldsymbol{S}}: \tilde{\boldsymbol{S}}\in\mathcal{S}, \tilde{\boldsymbol{J}_r}=\boldsymbol{J}_r, \tilde{\boldsymbol{J}}_p^{j}=\tilde{\boldsymbol{J}}_p^{j} \cup \{h\}, j\in \{1,\ldots,d_r\}, h\in J_f \right\}.
\end{equation}
	\item {\bf Removing a predictor covariate}: a predictor covariate is removed from one sub-regression of $\boldsymbol{S}$
\begin{equation}
\mathcal{V}_{p-}(\boldsymbol{S}) = \left\{\tilde{\boldsymbol{S}}: \tilde{\boldsymbol{S}}\in\mathcal{S}, \tilde{\boldsymbol{J}_r}=\boldsymbol{J}_r, \tilde{\boldsymbol{J}}_p^{j}=\tilde{\boldsymbol{J}}_p^{j} \backslash \{h\}, j\in \{1,\ldots,d_r\}, h\in J_f \right\}.
\end{equation}	
	\end{itemize}
